### 2014-11-13 tex/results.tex
argh

The prototype of  our~\symtxt{} algorithm is implemented as a new extension to SPF.
In addition to the operations presented in the Javalite
semantics (see \secref{sec:precise}), the implementation contains 
support for operations over
integers including symbolic representations. Examples of bytecode implemented in SPF to support the \symtxt{} algorithm
include:
(i) field access bytecodes, e.g., GETFIELD and ALOAD, to implement the 
field-access and summarize rules
in~\figref{fig:symInit} and~\figref{fig:fHeap}(a) respectively, (ii) the field
write bytecodes, e.g., PUTFIELD and ASTORE, to implement the
field-write rules in~\figref{fig:fHeap}(a), and (iii) equality checking of
references bytecodes, IF\_ACMPEQ and IF\_ACMPNE, to implement the
equals references-true and references-false rules in~\figref{fig:eqs}.
We also implement linear arithmetic operations on integers, and integer
comparison operations. We are currently working on adding support for
floating point operations, arrays, and bit-operations.  We use the
\texttt{jConstraints} library which provides support for handling heap
constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
solver~\cite{deMouraBjorner08Z3} as the underlying constraint solver. We
leverage the incremental solving feature in z3 in our experiments. We
also implement other optimizations that cache and re-use solutions to
previous constraints. These optimizations are an important part of our
implementation because only small portions of the heap constraint
changes from one state to another.

>>>>

The prototype of our~\symtxt{} algorithm is implemented as a new
extension to SPF.  In addition to the operations presented in the
Javalite semantics (see \secref{sec:precise}), the implementation
contains support for operations over integers.
% including symbolic
%representations.
% Examples of bytecode implemented in SPF to support the \symtxt{} algorithm
%include:
%(i) field access bytecodes, e.g., GETFIELD and ALOAD, to implement the 
%field-access and summarize rules
%in~\figref{fig:symInit} and~\figref{fig:fHeap}(a) respectively, (ii) the field
%write bytecodes, e.g., PUTFIELD and ASTORE, to implement the
%field-write rules in~\figref{fig:fHeap}(a), and (iii) equality checking of
%references bytecodes, IF\_ACMPEQ and IF\_ACMPNE, to implement the
%equals references-true and references-false rules in~\figref{fig:eqs}.
%We also implement linear arithmetic operations on integers, and integer
%comparison operations.
We are currently working on adding support for floating point
operations, arrays, and bit-operations.  We use the
\texttt{jConstraints} library which provides support for handling heap
constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
solver~\cite{deMouraBjorner08Z3} as the underlying constraint
solver. We leverage the incremental solving feature in z3 in our
experiments. We also implement other optimizations that cache and
re-use solutions to previous constraints. These optimizations are an
important part of our implementation because only small portions of
the heap constraint changes from one state to another.
